Cosmological constraints from the redshift dependence of the galaxy angular 2-point correlation function

### 2016-08-29 draft/draft0.tex
updates

\author{Xiao-Dong Li, }
\affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 130-722, Korea}
\author{Cheng Cheng, }
\affil{blahblahblah}
\author{Changbom Park,}
\affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 130-722, Korea}
\author{Cristiano G. Sabiu, Hyunbae Park,}
\affil{Korea Astronomy and Space Science Institute, Daejeon 305-348, Korea}
%\author{David H. Weinberg,}
%\affil{Department of Astronomy and CCAPP, The Ohio State University, 140 West 18th Avenue, Columbus, OH 43210, USA}
%\author{Donald P. Schneider,}
%\affil{Department of Astronomy and Astrophysics, The Pennsylvania State University, 
%University Park, PA 16802 }
%\affil{Institute for Gravitation and the Cosmos, The Pennsylvania State University, 
%University Park, PA 16802 }
\author{Juhan Kim\altaffilmark{1},}
\affil{Center for Advanced Computation, Korea Institute for Advanced Study, 85 Hoegi-ro, Dongdaemun-gu, Seoul 130-722, Korea}
\affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 130-722, Korea}
\and
\author{Sungwook E. Hong}
\affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 130-722, Korea}

@@

\section{Volume Effect}
\label{sec:Voleffect}

\begin{figure*}
   \centering{
   \includegraphics[height=8cm]{fig1_a.eps}
   \includegraphics[height=8cm]{fig1_b.eps}
   }
   \caption{\label{fig_xyquan}
   %Apparent distortion of objects in four wrongly assumed cosmologies, assuming a true cosmology of .
   The scaling in four wrongly assumed cosmologies ..., % $\Omega_m=0.41$, $w=-1.3$ and $\Omega_m=0.11$, $w=-0.7$, 
   assuming a true cosmology of $\Omega_m=0.26$, $w=-1$.
   Left panel shows a series of circular objects, measured by an observer located at the origin.
   Their true positions and shapes are plotted in blue dashed lines.
   The observer measures the redshifts of these objects, adopts the wrong cosmologies to compute the distance,
   and obtains wrong results (the red solid lines).
   %The red solid lines show their positions and shapes when the wrong cosmologies 
   % are assumed to compute distance from measured redshift.
   %The misestimation of angular diameter distance lead to wrong 
   Right panel shows the misestimation of angular diameter distance when the wrong cosmologies are adopted.
   %In our mock surveys we split the samples at $z=0.3$, 0.6, 0.9 and 1.2, as marked by the vertical lines.
   %measured by an observer located at the origin.
   %For reference, blue dashed squares show their shapes and positions in the true cosmology.
   }
   % Need a better plot to show angular size variation!!!
\end{figure*}

@@

The effects due to wrongly assumed cosmological parameters are shown in the upper panel of Figure \ref{fig_xyquan}.
Suppose that the true cosmology is a flat $\Lambda$CDM with present density parameter $\Omega_m=0.26$
and standard dark energy EoS $w=-1$.
If we were to distribute a series of perfect squares at various distances from 500 Mpc/h to ???? Mpc/h,
and an observer located at the origin were to measure their redshifts and compute their positions and shapes 
using redshift-distance relations of ??? incorrect cosmologies
\begin{enumerate}
 \item $\Omega_m=0.41$, $w=-1.3$,
 \item $\Omega_m=0.11$, $w=-0.7$,
\end{enumerate}
the shapes of the squares appear distorted (AP effect),
and their volumes are changed (volume effect).
In the cosmological model (ii) with $\Omega_m=0.11$, $w=-0.7$, we see a stretch of the shape in the line of sight (LOS) direction 
(hereafter ``LOS shape stretch'')
and magnification of the volume (hereafter ``volume magnification''), 
while in the model with $\Omega_m=0.41$, $w=-1.3$, we see opposite effects of LOS shape compression and volume shrinkage.

In the lower panel of Figure \ref{fig_xyquan}, we plot the $\frac{\Delta r_{\bot, \rm wrong}}{\Delta r_{\bot, \rm true}}$ redshift. 
In cosmology (i), both quantities have values less than 1, 
indicating LOS shape compression and volume shrink.
The effect in cosmology (ii) is slightly more subtle. At low redshift, the effect of dark energy is important, 
and there is LOS shape compression and volume reduction due to the quintessence like dark energy EoS.
However, at higher redshift the role of dark matter is more important, and we see LOS shape stretch and volume magnification due to the small $\Omega_m$.

More importantly, Figure \ref{fig_xyquan} highlights the redshift dependence of the AP and volume effects. 
For example, in the cosmology with $\Omega_m=0.41$, $w=-1.3$, 
both the LOS shape stretch and volume magnification become more significant with increasing redshift.
In the cosmology with $\Omega_m=0.11$, $w=-0.7$,
not only do the magnitudes of the effects evolve with redshift,
but there is also a turnover from LOS shape compression and volume shrink at lower redshift to LOS shape stretch and volume magnification at higher redshift.s

@@

@@

@@

\begin{figure*}
   \centering{
%   \includegraphics[width=14cm]{fig5.eps}
   %\includegraphics[width=14cm]{Tpcf--contour.eps}
   }
   \caption{
    \label{fig_2pcfcon} 
    2D contour map of measured $\xi$ as a function of $\mu$ and $s$, from the six redshift bins of LOWZ and CMASS samples 
      in the cosmology of $\Omega_m=0.31$ $\Lambda$CDM model.
    The black dashed lines mark the scales 6\ $h^{-1}$Mpc $\leq s\leq$ 40\ $h^{-1}$Mpc.
    %The correlation functions have rather large values on small sales such as $s=5$ $h^{-1}$Mpc,
    %  and monotonically decreases to smaller values on larger scales due to weaker clustering.
    The contour lines are not horizontal due to the effects of peculiar velocity.
    The FOG and Kaiser effects clearly manifest themselves through the tilting of contour 
     lines where $1-\mu \rightarrow 0$ and $1-\mu \gtrsim0.1$, respectively.
    The six contour maps have rather similar appearance, implying small redshift evolution of $\xi$.
   }
      %The redshift density distribution of the BOSS DR12 galaxy samples, assuming a $\Lambda$CDM cosmology with $\Omega_m=0.31$.
      %The blue and green solid histograms show the distribution of LOWZ and CMASS galaxies respectively. 
      %The vertical dashed lines define the 6 redshift bins that are used to cut the samples.   }
\end{figure*}

@@

\begin{figure*}
   \centering{
   \includegraphics[width=16cm]{fig4.eps}
   \includegraphics[width=16cm]{fig5.eps}
   }
   \caption{\label{fig_sys}
  Systematic effects.
   }
\end{figure*}
\subsection{Cosmological Constraints}

>>>>

\author{Xiao-Dong Li, }
\affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 130-722, Korea}
\author{Cheng Cheng, }
\affil{Kavli Institute for Theoretical Physics China, Institute of Theoretical Physics, Chinese Academy of Sciences, Zhong Guan Cun Street 55\#, Beijing, 100190, P.R. China}
\affil{University of Chinese Academy of Sciences, P.R. China}
\author{Changbom Park,}
\affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 130-722, Korea}
\author{Cristiano G. Sabiu, Hyunbae Park,}
\affil{Korea Astronomy and Space Science Institute, Daejeon 305-348, Korea}
%\author{David H. Weinberg,}
%\affil{Department of Astronomy and CCAPP, The Ohio State University, 140 West 18th Avenue, Columbus, OH 43210, USA}
%\author{Donald P. Schneider,}
%\affil{Department of Astronomy and Astrophysics, The Pennsylvania State University, 
%University Park, PA 16802 }
%\affil{Institute for Gravitation and the Cosmos, The Pennsylvania State University, 
%University Park, PA 16802 }
\author{Juhan Kim\altaffilmark{1},}
\affil{Center for Advanced Computation, Korea Institute for Advanced Study, 85 Hoegi-ro, Dongdaemun-gu, Seoul 130-722, Korea}
\affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 130-722, Korea}
\and
\author{Sungwook E. Hong}
\affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 130-722, Korea}

@@

\section{Geometric deformation when }
\label{sec:Voleffect}

\begin{figure*}
   \centering{
   \includegraphics[height=8cm]{fig1_a.eps}
   \includegraphics[height=8.5cm]{fig1_b.eps}
   }
   \caption{\label{fig_xyquan}
   %Apparent distortion of objects in four wrongly assumed cosmologies, assuming a true cosmology of .
   The scaling in four wrongly assumed cosmologies ..., % $\Omega_m=0.41$, $w=-1.3$ and $\Omega_m=0.11$, $w=-0.7$, 
   assuming a true cosmology of $\Omega_m=0.26$, $w=-1$.
   Left panel shows a series objects distributes as five perfect squares, measured by an observer located at the origin.
   Their true positions and shapes are plotted in blue dashed lines.
   The observer measures the redshifts of these objects, adopts the wrong cosmologies to compute the distance,
   and obtains wrong results (the red solid lines).
   %The red solid lines show their positions and shapes when the wrong cosmologies 
   % are assumed to compute distance from measured redshift.
   %The misestimation of angular diameter distance lead to wrong 
   Right panel shows the misestimation of angular diameter distance when the wrong cosmologies are adopted.
   %In our mock surveys we split the samples at $z=0.3$, 0.6, 0.9 and 1.2, as marked by the vertical lines.
   %measured by an observer located at the origin.
   %For reference, blue dashed squares show their shapes and positions in the true cosmology.
   }
   % Need a better plot to show angular size variation!!!
\end{figure*}

@@

The effects due to wrongly assumed cosmological parameters are shown in the upper panel of Figure \ref{fig_xyquan}.
Suppose that the true cosmology is a flat $\Lambda$CDM with present density parameter $\Omega_m=0.26$
and standard dark energy EoS $w=-1$.
If we were to distribute a series of perfect squares at various distances from 500 Mpc/h to 3\,000 Mpc/h,
and an observer located at the origin were to measure their redshifts and compute their positions and shapes 
using redshift-distance relations of four incorrect cosmologies
\begin{eqnarray}
 & &{\rm (i)}.\ \Omega_m=0.40,\ w=-1.0, \nonumber \\ 
 & &{\rm (ii)}.\ \Omega_m=0.15,\ w=-1.0, \nonumber\\ \noindent
 & &{\rm (iii)}.\ \Omega_m=0.26,\ w=-0.5,\nonumber\\ \noindent
 & &{\rm (iv)}.\ \Omega_m=0.26,\ w=-1.5, \nonumber \noindent
\end{eqnarray}
the shapes of the squares appear distorted (AP effect),
and their volumes are changed (volume effect).
In the cosmological models in model (i,iii) we see a compression of size (in both angular and LOS direction)
and the degree of compression increases with increasing distance,
while in models (ii,iv) we see stretch of size whose degree also evolves with redshift.
Thus, when wrong cosmological parameters are adopted,
the apparent size of objects are distorted, and the magnitude of distortion also varies with redshift.

In this paper we will use the galaxy angular 2pCF to probe the redshift dependence of the distortion in angular direction.
In the right panel of Figure \ref{fig_xyquan} we plot the redshift dependence of the change in angular size, 
${\Delta r_{\bot, \rm wrong}}/{\Delta r_{\bot, \rm true}}$, in the four wrong cosmologies.
In all cosmologies, there is clear evolution of ${\Delta r_{\bot, \rm wrong}}/{\Delta r_{\bot, \rm true}}$ 
in the redshift range $0<z<2$.
E.g., when use the quintessence cosmology 
$\Omega_m=0.26,\ w=-0.5$ to infer the postions of objects,
the angular size is underestimated by 
%12.5\%, 17.7\%, 20.1\%, 21.3\%
8.9\%, 12.3\%, 13.6\%, 14.1\% 
at $z=0.5,1,1.5,2$.

@@

\section{Galaxy angular 2pCF}

\subsection{Galaxy distribution at different redshifts}

The left panels of Figure \ref{fig_scatter} show the $x,y$ coordinates of galaxies in a 
$260 h^{-1} {\rm Mpc} \times 130 h^{-1} {\rm Mpc} \times 105 h^{-1} {\rm Mpc}$ volume, 
taken from the five snapshots.
The gravitational growth of structures with decreasing redshift is clearly shown.
We display all mock galaxies with $M> 3.0 \times 10^{11} \hMsun$.
At lower redshift, galaxies become more massive, so they are more galaxies satisfying the threshold.

If one adopts a wrong cosmology to compute galaxy positions, there would be a scaling of the galaxy distribution.
In the left panel we show the case when a wrong set of parameters $\Omega_m=0.05,\ w=-1.5$ is assumed,
leading to large upscaling of $25.6\%,47.3\%,62.2\%,71.7\%$ at redshifts $z=0.5,1.0,1.5,2.5$.

Compared with the true galaxy distribution, the apparent distribution inferred by wrong set of parameters
show clear evolution with redshift due to the different scaling at different redshifts.
In case of Figure \ref{fig_scatter}, the apparent size of large scale structures increases with redshift.

The growth of structure also make the size of structures evolves with redshift.
In the next subsection we will discuss how to distinguish these two effects in the galaxy angular 2pCF.

\begin{figure*}
   \centering{
   %\includegraphics[height=5.9cm]{fig8_0.eps}
   %\includegraphics[height=5.9cm]{fig8_wrongcos_0.eps}
   \includegraphics[width=16cm]{fig2.eps}
   }
   \caption{\label{fig_scatter}
  blah
   }
   % Need a better plot to show angular size variation!!!
\end{figure*}

\subsection{Galaxy angular 2pCF at different redshifts}

\begin{figure*}
   \centering{
   \includegraphics[width=16cm]{fig4.eps}
   \includegraphics[width=16cm]{fig5.eps}
   }
   \caption{\label{fig_sys}
  Systematic effects.
   }
\end{figure*}

\section{cosmological constraint}

@@

%\begin{minipage}{0.9\linewidth}
%\includegraphics[width= 0.3\linewidth]{fig8_0.eps}
%\caption{\label{fig8} hahaha}
%\end{minipage}

@@

\begin{figure*}
   \centering{
%   \includegraphics[width=14cm]{fig5.eps}
   \includegraphics[width=14cm]{fig9.eps}
   }
   \caption{
    \label{fig_2pcfcon} 
    2D contour map of measured $\xi$ as a function of $\mu$ and $s$, from the six redshift bins of LOWZ and CMASS samples 
      in the cosmology of $\Omega_m=0.31$ $\Lambda$CDM model.
    The black dashed lines mark the scales 6\ $h^{-1}$Mpc $\leq s\leq$ 40\ $h^{-1}$Mpc.
    %The correlation functions have rather large values on small sales such as $s=5$ $h^{-1}$Mpc,
    %  and monotonically decreases to smaller values on larger scales due to weaker clustering.
    The contour lines are not horizontal due to the effects of peculiar velocity.
    The FOG and Kaiser effects clearly manifest themselves through the tilting of contour 
     lines where $1-\mu \rightarrow 0$ and $1-\mu \gtrsim0.1$, respectively.
    The six contour maps have rather similar appearance, implying small redshift evolution of $\xi$.
   }
      %The redshift density distribution of the BOSS DR12 galaxy samples, assuming a $\Lambda$CDM cosmology with $\Omega_m=0.31$.
      %The blue and green solid histograms show the distribution of LOWZ and CMASS galaxies respectively. 
      %The vertical dashed lines define the 6 redshift bins that are used to cut the samples.   }
\end{figure*}

@@

\subsection{Cosmological Constraints}
